\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% EXPERIENCE A
%====================
\subsection{{Software Engineer \hfill Mar 2022 --- Present}}
\subtext{AvantStay \hfill Remote - LA, United States}
\vspace{1mm}
\begin{justify}
As part of Avantstay's operations team, I develop and maintain internal systems that streamline key services like cleaning, maintenance, and guest support for home bookings. I build features for our web platform and support a mobile app used by field teams and vendors. Additionally, I collaborate with other teams on the main website and systems for homeowners.
\end{justify}
\vspace{1mm}

%====================
% EXPERIENCE B
%====================
\subsection{{Software Engineer \hfill Oct 2021 --- Mar 2022}}
\subtext{Popstand \hfill Remote - LA, United States}
\vspace{1mm}
\begin{justify}
At Popstand, I led the development of an NFT marketplace on the Flow Blockchain, collaborating with the client’s team to deliver new features and ensure smooth NFT launches. I also participated in client meetings to gather feedback, present updates, and supported developers with project challenges.
\end{justify}
\vspace{1mm}

%====================
% EXPERIENCE C
%====================
\subsection{{Software Engineer \hfill Jul 2020 --- Oct 2021}}
\subtext{JungleDevs \hfill Florianópolis, Brazil}
\vspace{1mm}
\begin{justify}
Jungle Devs, now rebranded as Olby, was a software house where I developed tailored solutions to meet the unique needs of clients across various industries. I collaborated with cross-functional teams to design intuitive, high-performance interfaces, ensuring seamless user experiences. Additionally, I mentored fellow developers, offering guidance on best practices and solving technical challenges, which boosted team productivity and improved project outcomes.
\end{justify}
\vspace{1mm}

%====================
% EXPERIENCE D
%====================
\subsection{{Software Engineer Intern \hfill Jul 2019 --- Jun 2020}}
\subtext{JungleDevs \hfill Florianópolis, Brazil}
\vspace{1mm}
\begin{justify}
I was an intern at JungleDevs, participating in the Academy internship program, designed to cultivate new talent in software development. Throughout the program, I focused on the frontend stack, studying key frameworks and market patterns. Additionally, I had the opportunity to collaborate on real client projects, where I applied the knowledge and skills I gained during the internship.
\end{justify}
\vspace{1mm}

%====================
% EXPERIENCE E
%====================
\subsection{{Software Developer Intern \hfill Aug 2018 --- Jun 2019}}
\subtext{Federal University of Santa Catarina \hfill Florianópolis, Brazil}
\vspace{1mm}
\begin{justify}
I was involved in the initial stages of developing a new academic system for university students and staff. As fullstack developers, we worked with Ruby on Rails for the backend and Vue.js for the frontend
\end{justify}




\end{document}
